---
title: "child_merge_heatmaps_bm_2"
author: "Mohamed_Shoeb"
date: "1/31/2022"
output: html_document
---
## bind smoothed heatmaps
```{r}
#list of SingleCellExperiments with tradeseq and slingshot results
sim_obj_list <- list(traj = sim_traj,
                     xie = sim_xie_bm,
                     ballesteros = sim_ballesteros_bm,
                     neutrotime = sim_neutime_bm,
                     abs = sim_abs,
                     suo = sim_suo_neut_homo_bm,
                     tabula_sapiens = sim_tabula_sapiens_neut_homo
                     )
#annotations
dataset_species_annot <- data.frame(dataset = names(sim_obj_list),
                                    species = c("zebrafish",
                                                rep("mouse", 3),
                                                rep("human", 3)))

#aggregated scaled expression matrices of all the datasets
aggr_avg_traj_scaled <- aggr_pseud_avg(seurat_obj=srt_traj,
                                ss_df=ss_df_traj,
                                genes=diff_traj$gene_symbol) %>% 
  t() %>% 
  scale() %>% 
  t() %>% 
  as.data.frame()

aggr_avg_xie_scaled <- aggr_pseud_avg(seurat_obj=subset(xie_mm_neut_homo,tissue %in% c("WT_BM", "WT_BM_C-kit+Gr1")),
                                 ss_df=ss_df_xie_bm,
                                 genes=diff_traj$gene_symbol) %>% 
  t() %>% 
  scale() %>% 
  t() %>% 
  as.data.frame() 

aggr_avg_ballesteros_scaled <- aggr_pseud_avg(seurat_obj=subset(ballesteros_obj_neut_homo,tissue %in% c("BM")),
                                 ss_df=ss_df_ballesteros_bm,
                                 genes=diff_traj$gene_symbol) %>% 
  t() %>% 
  scale() %>% 
  t() %>% 
  as.data.frame() 

aggr_avg_neutime_scaled <- aggr_pseud_avg(seurat_obj=subset(neutime_obj_homo,tissue %in% c("marrow")),
                                 ss_df=ss_df_neutime_bm,
                                 genes=diff_traj$gene_symbol) %>% 
  t() %>% 
  scale() %>% 
  t() %>% 
  as.data.frame() 

aggr_avg_abs_scaled <- aggr_pseud_avg(seurat_obj=abs_neut_homo,
                                ss_df=ss_df_abs,
                                genes=diff_traj$gene_symbol) %>% 
  t() %>% 
  scale() %>% 
  t() %>% 
  as.data.frame() 

aggr_avg_suo_scaled <- aggr_pseud_avg(seurat_obj=subset(suo_neut_homo,organ %in% c("BM")),
                                ss_df=ss_df_suo_neut_bm,
                                genes=diff_traj$gene_symbol) %>% 
  t() %>% 
  scale() %>% 
  t() %>% 
  as.data.frame() 

aggr_avg_tabula_sapiens_scaled <- aggr_pseud_avg(seurat_obj=subset(tabula_sapiens_neut_homo,tissue_in_publication %in% c("Bone_Marrow")),
                                ss_df=ss_df_tabula_sapiens_neut_bm,
                                genes=diff_traj$gene_symbol) %>% 
  t() %>% 
  scale() %>% 
  t() %>% 
  as.data.frame() 

all_aggr_expr_lst <- list(traj = aggr_avg_traj_scaled,
                          xie = aggr_avg_xie_scaled,
                          ballesteros = aggr_avg_ballesteros_scaled,
                          neutrotime = aggr_avg_neutime_scaled,
                          abs = aggr_avg_abs_scaled,
                          suo = aggr_avg_suo_scaled,
                          tabula_sapiens = aggr_avg_tabula_sapiens_scaled
                         )
#common genes
all_aggr_expr_genes <- all_aggr_expr_lst %>% 
  lapply(function(x) x %>% na.omit %>% rownames)%>% #remove genes that are NaN because they weere all zeros across the bins
  c(list(rownames(ramirez_norm))) %>% #common genes with ramirez
  purrr::reduce(intersect)

#merge all datasets
all_aggr_expr_df <- lapply(all_aggr_expr_lst,function(df){
  df[all_aggr_expr_genes,]
  }) %>% 
  do.call(cbind, .) %>% 
  as.data.frame()

#time point dataset annotation
aggr_timepoints_annot <- sapply(all_aggr_expr_lst, ncol) %>%
  enframe(name = "dataset", value = "n") %>% 
  left_join(dataset_species_annot) %>% 
  uncount(n) %>% 
  group_by(dataset) %>% 
  mutate(pseudotime_bin = paste0(dataset, "_", 1:n()),
         species = factor(species,levels = unique(dataset_species_annot$species))) %>% 
  ungroup() %>% 
  column_to_rownames("pseudotime_bin")

colnames(all_aggr_expr_df) <- rownames(aggr_timepoints_annot)
```

Average expression along bins of maturation trajectories
```{r}
all_aggr_expr_avg_lst <- list(traj = aggr_avg_traj,
                          xie = aggr_avg_xie,
                          ballesteros = aggr_avg_ballesteros,
                          neutrotime = aggr_avg_neutime,
                          abs = aggr_avg_abs,
                          suo = aggr_avg_suo,
                          tabula_sapiens = aggr_avg_tabula_sapiens
                         )

all_aggr_expr_avg_genes <- all_aggr_expr_avg_lst %>% 
  lapply(function(x) x %>% na.omit %>% rownames)%>% #remove genes that are NaN because they weere all zeros across the bins
  purrr::reduce(intersect)

#merge all datasets
all_aggr_expr_avg_df <- lapply(all_aggr_expr_avg_lst,function(df){
  df[all_aggr_expr_genes,]
  }) %>% 
  do.call(cbind, .) %>% 
  as.data.frame()

colnames(all_aggr_expr_avg_df) <- rownames(aggr_timepoints_annot)
```

## Order genes in the cross-species heatmap
```{r}
#seriate genes based on all dataset
o <- seriate(all_aggr_expr_df , method = "PCA")
gene_ser <- all_aggr_expr_df[get_order(o, 1),] %>% rownames()
#
gene_order_ortho <- gene_clusters_avg_hc[gene_ser,,drop = FALSE] %>%
  rownames_to_column("gene_symbol")%$%
  split(gene_symbol, module) %>%
  unlist(use.names=FALSE)
```

## Calculate gene cross-correlation between mammilian systems (mouse and human) and zebrafish 
```{r}
#split datasets matrices
ls_aggr_expr <- lapply(dataset_species_annot$dataset,function(dataset_x){
  dataset_t <- aggr_timepoints_annot$dataset==dataset_x
   all_aggr_expr_df[gene_order_ortho,dataset_t]
   }) 
names(ls_aggr_expr) <- dataset_species_annot$dataset

#calculate cross-correlation
## number of lags to be shited to the left and right 
n_lags <- min(sapply(ls_aggr_expr, ncol))-1 #at least one bin between trajectories
## Genes cross-correlation dataframe
ccf_aggr <- lapply(gene_order_ortho,function(gene){
  # Get gene expression in zebrafish trajectory
  traj_gene_expr <- ls_aggr_expr[["traj"]][gene,] %>% unlist
  # Get gene expression in other trajectories, then calculate it's cross-correlation to zebrafish
  lapply(ls_aggr_expr[c(-1)], function(dataset){
    dataset_gene_expr <- dataset[gene,] %>% unlist
    ccf(dataset_gene_expr,traj_gene_expr,n_lags,plot = FALSE)$acf
    })%>%
  #bind cross correlation results across datasets, then add lags and gene name information
  do.call(cbind,.) %>% 
    as.data.frame %>% 
    mutate(lags = -n_lags:n_lags) %>% 
    pivot_longer(-lags, names_to = "dataset", values_to = "correlation") %>% 
    mutate(gene = gene)
  })%>%
  do.call(rbind,.)

## Genes cross-correlation dataframe based on different references
ccf_aggr_all <- lapply(gene_order_ortho,function(gene){
  lapply(dataset_species_annot$dataset, function(ref_dataset){
  # Get gene expression in reference trajectory
  ref_gene_expr <- ls_aggr_expr[[ref_dataset]][gene,] %>% unlist
  # Get gene expression in other trajectories, then calculate it's cross-correlation to zebrafish
  lapply(ls_aggr_expr, function(dataset){
    dataset_gene_expr <- dataset[gene,] %>% unlist
    ccf(dataset_gene_expr,ref_gene_expr,n_lags,plot = FALSE)$acf
    })%>%
    do.call(cbind,.)%>% 
    as.data.frame %>% 
    mutate(lags = -n_lags:n_lags,
           gene = gene,
           ref_dataset = ref_dataset) 
           })%>%
  #bind cross correlation results across datasets, then add lags and gene name information
  do.call(rbind,.) %>% 
    as.data.frame %>%
    pivot_longer(-c(lags,gene, ref_dataset),
                 names_to = "query_dataset",
                 values_to = "correlation")
  })%>%
  do.call(rbind,.) %>%
  mutate(ref_dataset = factor(ref_dataset,levels = dataset_species_annot$dataset),
         query_dataset = factor(query_dataset,levels = dataset_species_annot$dataset))

#summarize cross-correlation results
##For each gene, in each dataset, get the lag with maximum correlation
ccf_max_aggr <- ccf_aggr_all %>%
  filter(ref_dataset=="traj" & query_dataset!="traj")%>%
  group_by(gene,query_dataset) %>% 
  filter(correlation == max(correlation)) %>% 
  ungroup()%>%
  mutate(dataset=query_dataset,
         query_dataset = NULL,
         ref_dataset=NULL)
##gene summary statistics across datasets
ccf_df_aggr <- ccf_max_aggr %>%
  group_by(gene) %>%
  summarize(lag_var = var(lags),
            lag_med = median(lags),
            cor_var = var(correlation),
            cor_med = median(correlation)) %>% 
  column_to_rownames("gene")
##matrix of maximum correlation lag
ccf_all <- ccf_max_aggr %>% 
  dplyr::select(gene,dataset, lags) %>% 
  pivot_wider(names_from = "dataset",
              values_from = "lags") %>%
  column_to_rownames("gene") 
ccf_all <- ccf_all[,dataset_species_annot$dataset[-1]]
##average lags across mouse and human datasets
ccf_all_mean_species <- ccf_all%>% 
  mutate(mouse = apply(.[,1:3],1,mean),
         human = apply(.[,4:6],1,mean)) %>% 
  dplyr::select(mouse, human)
```

## cross-correlation with different references summary plot
```{r}
module_genes_ccf_ref_lst <-ccf_aggr_all %>%
 group_by(ref_dataset, query_dataset, gene) %>%
 filter(correlation == max(correlation)) %>%
 ungroup() %>%
 left_join(gene_clusters_lst %>% stack %>% dplyr::rename("module" = "ind"), by = c("gene"="values")) %>% 
 split(., .$module)

module_genes_ccf_ref_aggr <- module_genes_ccf_ref_lst %>%
 lapply(function(module){
   module %>%
    group_by(ref_dataset, query_dataset)%>%
    summarize(x = median(lags))%>%
    pivot_wider( names_from = "query_dataset", values_from= "x") %>%
    ungroup() %>%
    column_to_rownames("ref_dataset")
    })
```

Gene-number sensitivity analysis
Supplementary Figure 7cde
```{r, eval = FALSE}
#list of gene number
top_n_genes <- seq(50,nrow(diff_traj),50)
top_n_genes <- c(top_n_genes, nrow(diff_traj))
genes_list <- lapply(top_n_genes, function(x) {
  head(diff_traj$gene_symbol,x)
  })
names(genes_list) <- paste0("top_",top_n_genes,"_genes")

#aggregated lags matrices for each gene number
mat_top_n_list <- lapply(genes_list, function(genes){
  module_genes_ccf_ref_lst <-ccf_aggr_all %>%
    filter(gene %in% genes)%>%
    group_by(ref_dataset, query_dataset, gene) %>%
    filter(correlation == max(correlation)) %>%
    ungroup() %>%
    left_join(gene_clusters_lst %>% stack %>% dplyr::rename("module" = "ind"), by = c("gene"="values")) %>% 
    split(., .$module)

  module_genes_ccf_ref_aggr <- module_genes_ccf_ref_lst %>%
  lapply(function(module){
    mat <- module %>%
      group_by(ref_dataset, query_dataset)%>%
      summarize(x = median(lags))%>%
      pivot_wider( names_from = "query_dataset", values_from= "x") %>%
      ungroup() %>%
      column_to_rownames("ref_dataset")

    mat[lower.tri(mat)] <- mat[lower.tri(mat)]*-1
    mat
      })
  
  module_genes_ccf_ref_aggr
})  

#heatmap annotations
col_fun = circlize::colorRamp2(-25:25,
                               colorRampPalette( grDevices::hcl.colors(9,"RdYlBu"))(51) %>% rev())
row_annot <- rowAnnotation(species = dataset_species_annot$species,
                              col = list(species = column_annot_cols$species),
                              show_legend = FALSE,
                              show_annotation_name = FALSE,
                              annotation_name_gp = ,
                              simple_anno_size = unit(0.35, "cm"))
col_annot <- HeatmapAnnotation(species = dataset_species_annot$species,
                              col = list(species = column_annot_cols$species),
                              show_legend = FALSE,
                              show_annotation_name = FALSE,
                              annotation_name_gp = ,
                              simple_anno_size = unit(0.35, "cm"))

#hierarchical clustering list of datasets 
hclust_top_n_list <- lapply(mat_top_n_list, function(module_aggr_top_n){
  module_genes_ccf_ref_aggr <- module_aggr_top_n
  hclust_top_n_lst <- lapply(module_genes_ccf_ref_aggr, function(mat){
  #hclust_obj <- mat %>% dist %>% hclust %>% as.dendrogram %>% dendsort %>% as.hclust
  hclust_obj <- mat %>% dist %>% hclust
  })
  })


#calculate cophenetic distance
cophenetic_lst <- lapply(names(hclust_top_n_list), function(top_genes_name){
  top_genes <-hclust_top_n_list[[top_genes_name]]
  lapply(names(top_genes), function(module_name){
    module <- top_genes[[module_name]]
    x <- cophenetic(module) %>% as.matrix
    x[lower.tri(x)] <- NA
    x %>%
      as.data.frame() %>% 
      rownames_to_column("row") %>%
      pivot_longer(-row, names_to = "col") %>%
      as.data.frame %>%
       filter(!is.na(value),row != col) %>%
        arrange(row)%>%
        dplyr::rename(!!top_genes_name:="value") %>%
        mutate_if(is.factor, as.character)
        }) %>%
        setNames(.,names(top_genes))
      }) %>%
      setNames(.,names(hclust_top_n_list))

#heatmaps of cophenetic distance

modules <- c("module_1", "module_2", "module_3")
for(module_i in modules){
  pdf(glue::glue("heatmap_cophenetic_{module_i}.pdf"),width = 10, height = 7)

  #unclustered cophenetic distance
  lapply(cophenetic_lst,`[[`,module_i) %>% purrr::reduce(full_join, by = c("row", "col")) %>%
  tidyr::unite("pair", row, col) %>%
  column_to_rownames("pair") %>%
  ComplexHeatmap::Heatmap(col = colorRampPalette( grDevices::hcl.colors(9,"YlGnBu"))(100),
                          name = "cophenetic\ndistance",
                          cluster_rows = FALSE,
                          cluster_columns = FALSE,
                          column_names_gp = gpar(fontsize = 8)) %>% 
                          print()

  #clustered cophenetic distance
  lapply(cophenetic_lst,`[[`,module_i) %>% purrr::reduce(full_join, by = c("row", "col")) %>%
  tidyr::unite("pair", row, col) %>%
  column_to_rownames("pair") %>%
  ComplexHeatmap::Heatmap(col = colorRampPalette( grDevices::hcl.colors(9,"YlGnBu"))(100),
                            name = "cophenetic\ndistance",
                          cluster_rows = TRUE,
                          cluster_columns = FALSE,
                          column_names_gp = gpar(fontsize = 8))%>% 
                          print()
dev.off()
}

#heatmap of cophenetic distances at n = 1500
cophenetic_1500_df <- cophenetic_lst$top_1500_genes %>%
  bind_rows(.id = "module_i")%>%
  tidyr::unite("pair", row, col, sep = "-")%>%
  pivot_wider(names_from = module_i, values_from = top_1500_genes)%>%
  column_to_rownames("pair")
pair_names <- cophenetic_1500_df %>% rownames %>%str_split("-",simplify=TRUE)
names_species <- dataset_species_annot %$%setNames(species, dataset)
pair_species_Pair_1 <- names_species[pair_names[,1]]
pair_species_Pair_2 <- names_species[pair_names[,2]]

cophenetic_row_annot <- rowAnnotation(Pair_1 = pair_species_Pair_1,
                                      Pair_2  =  pair_species_Pair_2 ,
                              col = list(Pair_1 = column_annot_cols$species[pair_species_Pair_1],
                                          Pair_2  = column_annot_cols$species[pair_species_Pair_2 ]),
                              show_legend = c(Pair_2 = FALSE),
                              show_annotation_name = TRUE,
                              annotation_name_side = "top",
                              annotation_legend_param = list(Pair_1 = list(title = "Species")) ,
                              simple_anno_size = unit(0.35, "cm"))

pdf(glue::glue("cophenetic_1500_heatmap.pdf"),width = 10, height = 7)
cophenetic_1500_df %>%
  ComplexHeatmap::Heatmap(
                column_title = "",
                column_names_side = "top",
                column_names_rot = 0,
                column_names_centered = TRUE,
                #rect_gp = gpar(col = "white", lwd = 0.5),
                name = "Cophenetic\ndistance",
                  col =  grDevices::hcl.colors(30,"Viridis"),
                  cluster_rows = TRUE,
                  cluster_columns = FALSE,
                  row_dend_reorder = TRUE,
                    row_names_gp = gpar(fontsize = 14),
                    left_annotation = cophenetic_row_annot,
                    #top_annotation = col_annot
                    )
dev.off()

#separate heatmap of aggregated modules lags for each gene number
pdf("heatmap_module_cross_correlation_dtw_top_n.pdf",width = 20, height = 7)
lapply(names(hclust_top_n_list), function(top_genes){
    x <- cophenetic_lst[[top_genes]] %>% lapply(`[[`,3) %>% sapply(max)
    x1 <- x/max(x)*10
  hclust_modules_list <- hclust_top_n_list[[top_genes]]
  ht_modules <- lapply(names(hclust_modules_list), function(module_name){
    mat <- mat_top_n_list[[top_genes]][[module_name]]
    hclust_obj <- hclust_modules_list[[module_name]]

    if(module_name == "module_3"){
    row_annot@anno_list$species@show_legend <- TRUE
    }else{
    row_annot@anno_list$species@show_legend <- FALSE
    }

    ht <- ComplexHeatmap::Heatmap(mat,
                  column_title = str_replace(module_name,"module_","M"),
                name = "Median lags",
                  col =  col_fun,
                show_heatmap_legend = ifelse(module_name == "module_3", TRUE, FALSE),
                  cluster_rows = hclust_obj,
                  cluster_columns = hclust_obj,
                  column_dend_reorder = TRUE,
                  row_dend_reorder = TRUE,
                cell_fun = function(j, i, x, y, w, h, col) { # add text to each grid
                    grid.text(round(mat[i, j],2), x, y,gp = gpar(fontsize = 12))},
                    row_names_gp = gpar(fontsize = 14),
                    left_annotation = row_annot,
                    top_annotation = col_annot,
                    column_dend_height = unit(x1[module_name], "mm"))
  
    ht_grop <- grid.grabExpr({draw(ht);
                              decorate_column_dend("Median lags", {grid.yaxis(at = seq(0,ceiling(max(x)),length.out = 5))})
                              })                             
          })

  gridExtra::grid.arrange(ht_modules[[1]],
                          ht_modules[[2]],
                          ht_modules[[3]],
                          top = top_genes, ncol = 3)
  })

dev.off()

#Only show dendrograms separate heatmap of aggregated modules lags for each gene number
dend_annot <- HeatmapAnnotation(species = dataset_species_annot$species,
                              col = list(species = column_annot_cols$species),
                              show_legend = TRUE,
                              show_annotation_name = FALSE,
                              annotation_name_gp = ,
                              simple_anno_size = unit(0.5, "cm"))

pdf("heatmap_module_cross_correlation_dtw_top_1500_dendrogram_only.pdf",width = 9, height = 7)
lapply("top_1500_genes", function(top_genes){
    x <- cophenetic_lst[[top_genes]] %>% lapply(`[[`,3) %>% sapply(max)
    x1 <- x/max(x)*10
    hclust_modules_list <- hclust_top_n_list[[top_genes]]
    ht_modules <- lapply(names(hclust_modules_list), function(module_name){
      mat <- mat_top_n_list[[top_genes]][[module_name]]
      hclust_obj <- hclust_modules_list[[module_name]]

      if(module_name == "module_3"){
      dend_annot@anno_list$species@show_legend <- TRUE
      }else{
      dend_annot@anno_list$species@show_legend <- FALSE
      }

      ht <- ComplexHeatmap::Heatmap(mat,
                  height = 0,
                  width = 7 * unit(5, "mm"),
                  column_title = str_replace(module_name,"module_","M"),
                  name = "Median lags",
                    col =  col_fun,
                  show_heatmap_legend =FALSE,
                    cluster_rows = FALSE,
                    show_row_names= FALSE,
                    cluster_columns = hclust_obj,
                    column_dend_reorder = TRUE,
                    row_dend_reorder = TRUE,
                      row_names_gp = gpar(fontsize = 14),
                      #left_annotation = row_annot,
                      top_annotation = dend_annot,
                      column_dend_height = unit(x1[module_name], "mm"))
    
      ht_grop <- grid.grabExpr({draw(ht,padding = unit(c(ifelse(module_name == "module_3", 4.8, 0), 0, 0, 2), "mm"));
                                decorate_column_dend("Median lags", {grid.yaxis(at = seq(0,30,length.out = 5))})
                                })                             
            })

    gridExtra::grid.arrange(ht_modules[[1]],
                            ht_modules[[2]],
                            ht_modules[[3]],
                            top = top_genes, ncol = 3)
  })

dev.off()
```

## Line-point plots of maximum cross-correlation lags of all genes
Supplementary Figure 7b
```{r}
pdf("cross_correlation_all_1500.pdf",height = 30)
map(names(gene_clusters_lst), function(module_x){
  ccf_all[gene_order_ortho,] %>%
    rownames_to_column("gene_symbol") %>%
    mutate(gene_symbol = factor(gene_symbol, levels = rev(gene_symbol))) %>% 
        arrange(gene_symbol) %>% 
    pivot_longer(-gene_symbol, values_to = "lags", names_to = "dataset") %>% 
    mutate(species = ifelse(dataset %in% c("xie","ballesteros","neutrotime"), "mouse", "human")) %>% 
    left_join(gene_clusters_lst %>% stack %>% dplyr::rename("module" = "ind"), by = c("gene_symbol"="values")) %>% 
    filter(module == module_x) %>%
    mutate(gene_symbol = factor(gene_symbol, level = unique(gene_symbol)),
          species = factor(species, levels = c("mouse","human"))) %>% 
    ggplot()+
    geom_vline(xintercept=0, color = "grey80", lty = 2)+
    geom_line(aes(lags, gene_symbol,group = gene_symbol),
              size = 1,
              color = "grey90")+
    geom_point(aes(lags, gene_symbol, color = dataset, shape = dataset),
               size = 1)+
    facet_wrap(~species, ncol = 2)+
    scale_color_manual(values = c("traj" = "#54278f",
                                "xie" = "#d94801",
                                "ballesteros" = "#dd3497",
                                "neutrotime" = "#fc4e2a",
                                "abs" = "#253494",
                                "suo" = "#253494",
                                "tabula_sapiens" = "#253494",
                                "mouse" = "#fc4e2a",
                                "human" = "#253494"),
                     breaks = c("xie", "ballesteros","neutrotime", "abs", "suo", "tabula_sapiens"),
                     labels = c("Xie 2020", "Ballesteros 2020", "Grieshaber-Bouyer 2020", "Xie 2021", "Suo 2022", "Tabula sapiens 2022"))+
    scale_shape_manual(values = 1:6,breaks = c("xie", "ballesteros","neutrotime", "abs", "suo", "tabula_sapiens"),
                     labels = c("Xie 2020", "Ballesteros 2020", "Grieshaber-Bouyer 2020", "Xie 2021", "Suo 2022", "Tabula sapiens 2022"))+
    labs(title = c("module_1"="M1","module_2"="M2","module_3"="M3","module_4"="M4")[module_x],
         x = "Lags from zebrafish",
         y = "Gene symbol")+
    guides(colour = guide_legend(nrow = 3))+
    theme(legend.position = "bottom",
          axis.text.y = element_text(size = 8),
          axis.ticks.y = element_blank())
  })
dev.off()
```

## line plot of all cross-correlation lags of a selection of genes
Supplementary Figure 7a
```{r}
cc_genes <- c("cebpb", "mmp9", "tgfbi", "amd1", "pomp","txnipa")
pdf("cross_correlation_line_selection.pdf", height = 6, width = 7)
ccf_aggr_all %>% 
  filter(ref_dataset=="traj" & query_dataset!="traj")%>%
  left_join(dataset_species_annot, by=c("query_dataset"="dataset"))%>%
  filter(gene %in% cc_genes) %>% 
  mutate(species = factor(species, levels = c("mouse", "human"))) %>%
  ggplot(aes(lags, correlation, color = query_dataset))+
  geom_vline(xintercept = 0, color = "grey90")+
  geom_line()+
  facet_grid(gene ~ species, scales = "free_y")+
  scale_color_manual(name="",values = c("traj" = "#54278f",
                              "xie" = "#b30000",
                              "ballesteros" = "#d7301f",
                              "neutrotime" = "#ef6548",
                              "abs" = "#08519c",
                              "suo" = "#2171b5",
                              "tabula_sapiens" = "#4292c6",
                              "mouse" = "#fc4e2a",
                              "human" = "#253494"),
                    breaks = c("xie", "ballesteros","neutrotime", "abs", "suo", "tabula_sapiens"),
                    labels = c("Xie 2020", "Ballesteros 2020", "Grieshaber-Bouyer 2020", "Xie 2021", "Suo 2022", "Tabula sapiens 2022"))+
      guides(colour = guide_legend(nrow = 1, override.aes = list(size = 0.5)))+
  labs(y = "Cross correlation", x = "Lags from zebrafish")+
  theme(#aspect.ratio = 1/3,
        legend.position = "top",
        title =  element_text(size = 9,hjust = 0.5),
        strip.text = element_text(size = 10, hjust = 0.5),
        axis.text = element_text(size = 8),
        axis.title = element_text(size = 9),
        legend.text = element_text(size = 7),
        strip.background = element_blank())
dev.off()
```

